---
title: "Untitled"
author: "JRL"
date: "03/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(openxlsx)
install.packages("expss")
library(expss)
```


```{r taxa_assignment_table, echo=FALSE}
library(readxl)
(taxa_assignment_table <- read_excel("taxa_assignment_table.xlsx"))
View(taxa_assignment_table)

```
```{r list_contaminated_OTU, echo=FALSE}
(tot_read_PCR <- select(taxa_assignment_table, PCRCont) %>% 
  colSums())
(taxa_assignment_table %>% filter(PCRCont !=0) %>% 
  mutate(pct_cont_OTU_PCR = (PCRCont/tot_read_PCR)*100))
```

Only two OTU contaminated the samples at the PCR step (We have no contaminants in External contaminant sample)

```{r list_contaminated_OTU, echo=FALSE}
(tot_read_ExtCont <- select(taxa_assignment_table, ExtCont) %>% 
  colSums())
(taxa_assignment_table %>% filter(ExtCont !=0) %>% 
  mutate(ext_cont_OTU_PCR = (ExtCont/tot_read_PCR)*100))
```
```{r list_contaminated_OTU, echo=FALSE}
(tot_read_MockCom <- select(taxa_assignment_table, MockCom) %>% 
  colSums())
(taxa_assignment_table %>% filter(MockCom !=0) %>% 
  mutate(mock_com_OTU_PCR = (MockCom/tot_read_PCR)*100))
```

Only two OTU contaminated the samples at the PCR step (We have no contaminants in External contaminant sample)


```{r}
#First, we select the columns we want to work with : all the samples (grep function) and PCRCont (which function)
assignment_table_comp <- taxa_assignment_table[,c
                                          (which(colnames(taxa_assignment_table)=="PCRCont"),
                                            grep("[\\-]", colnames(taxa_assignment_table)))]
#We create a vector containing the name of the columns for the percentage of contamination. So the vector is 47 length
varnames <- paste(colnames(assignment_table_comp)[-1], "pct","cont", sep = "_")
#We calculate ther percentage, i.e. PCRCont reads divided by the reads in one sample for one contaminated OTU
calculated_pct <- ( assignment_table_comp$PCRCont / assignment_table_comp[,2:length(assignment_table_comp)]  ) * 100
#We rename the columns of the data frame 'calculated_pct' with the names we put in varnames
names(calculated_pct) <- varnames
#The result is a data frame with the name of the contaminatde OTU and the percentage of contamination for each sample
(res <- cbind(taxa_assignment_table[,c(1:7,
                                  which(colnames(taxa_assignment_table)=="PCRCont" ))],
                                calculated_pct) %>% 
      filter(PCRCont !=0)
)
```
```{r}
#First, we select the columns we want to work with : all the samples (grep function) and ExtCont (which function)
assignment_table_comp <- taxa_assignment_table[,c
                                          (which(colnames(taxa_assignment_table)=="ExtCont"),
                                            grep("[\\-]", colnames(taxa_assignment_table)))]
#We create a vector containing the name of the columns for the percentage of contamination. So the vector is 47 length
varnames <- paste(colnames(assignment_table_comp)[-1], "ext","cont", sep = "_")
#We calculate ther percentage, i.e. ExtCont reads divided by the reads in one sample for one contaminated OTU
calculated_pct <- ( assignment_table_comp$ExtCont / assignment_table_comp[,2:length(assignment_table_comp)]  ) * 100
#We rename the columns of the data frame 'calculated_pct' with the names we put in varnames
names(calculated_pct) <- varnames
#The result is a data frame with the name of the contaminatde OTU and the percentage of contamination for each sample
(res <- cbind(taxa_assignment_table[,c(1:7,
                                  which(colnames(taxa_assignment_table)=="ExtCont" ))],
                                calculated_pct) %>% 
      filter(ExtCont !=0)
)
```

```{r}
#First, we select the columns we want to work with : all the samples (grep function) and MockComt (which function)
assignment_table_comp <- taxa_assignment_table[,c
                                          (which(colnames(taxa_assignment_table)=="MockCom"),
                                            grep("[\\-]", colnames(taxa_assignment_table)))]
#We create a vector containing the name of the columns for the percentage of contamination. So the vector is 47 length
varnames <- paste(colnames(assignment_table_comp)[-1], "mock","com", sep = "_")
#We calculate ther percentage, i.e. PCRCont reads divided by the reads in one sample for one contaminated OTU
calculated_pct <- ( assignment_table_comp$MockCom / assignment_table_comp[,2:length(assignment_table_comp)]  ) * 100
#We rename the columns of the data frame 'calculated_pct' with the names we put in varnames
names(calculated_pct) <- varnames
#The result is a data frame with the name of the contaminatde OTU and the percentage of contamination for each sample
(res <- cbind(taxa_assignment_table[,c(1:7,
                                  which(colnames(taxa_assignment_table)=="MockCom" ))],
                                calculated_pct) %>% 
      filter(MockCom !=0)
)
```

These two OTU have contaminated the PCRCont samples. 

# Hilights wich OTU are the more biaised

## Number of samples overrating 100 % of contamination

```{r hilight}
# Change the Inf in NA
res <- na_if(res, Inf)
#Transpose the matrix so that we can easily play with the numbers
  (t_res <- data.frame(t(res[-c(1:7)])))
  list_colnames <- list()
  for (i in c(1:dim(res)[1])) {
    list_colnames[i] <- paste(res[i,1], res[i,2], res[i,3], res[i,4], res[i,5], res[i,6], res[i,7], sep ="_")
  }
  colnames(t_res) <- list_colnames
# Show the number of times samples have a contamination percentage higher than 100 %
(nb_hundred_samples <- 
    cbind(data.frame(rownames(t_res)),
          data.frame(count_row_if(function(x) x>=100, t_res))) %>% 
    rename("Samples" = 1, "Count" = 2) %>% 
    arrange(desc(Count))
)
  
# Add the average contamination of the sample
  
  
```


## Average contamination for each sample


```{r}
# The same for the otu
  
(nb_hundred_otu <- 
  cbind(data.frame(colnames(t_res)),
        data.frame(count_col_if(function(x) x>=100, t_res))) %>% 
  rename("OTU" = 1, "Count" = 2)%>%
  arrange(desc(Count))
)
```




